{ \fontfamily{ptm}\selectfont Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method }

### 2025-11-12 Notebook LaTEX/EB is the key to IAGP/main.tex
>w<, changes

            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}, 
            & x_k \approx_{\epsilon_k} T_{L_k}(y_k), 

@@

            & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 

@@

    \begin{proposition}[generic convergence rate under valid error schedule]\;\label{prop:inxt-apg-cnvg-generic}\\

@@

    \begin{proposition}[generic convergence rate of the gradient mapping]\;\label{prop:apg-cnvg-gm-generic}\\
            Cette proposition ira démontrer que ce séquence de ``Inexact Gradient Mapping" converge. \\
            N'oubliez pas de finir. 

    \end{proof}
    \par
    Now, it only remains to determine the sequence $\alpha_k$ to derive a type of convergence rate for the algorithm because from the above theorem, we have the convergence rate $\beta_k$ and, the error parameters $\epsilon_k, \rho_k$ both controlled by the sequence $(\alpha_k)_{k \ge 0}$.

@@

                \beta_k

@@

        \begin{proposition}[$\mathcal O(1/k^2)$ optimal convergence rate of the outer loop]\;\label{prop:opt-cnvg-outr-loop}\\

@@

@@

                \right)(F(x_k) - F(\bar x)), \text{where } \frac{\gamma}{2\tau} \in (0, 1)

@@

                \item\label{prop:inn-loop-lin-cnvg:item3} The duality gap has a linear convergence rate vy the inequality: 

@@

                \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. If we let $\tau = \lambda \Vert AA^\top\Vert$, then a sufficient number of iteration needed to achieve the optimality is given by: 
                    N'obliez pas de finir! 

@@

        \end{remark}
        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]\;\\
            A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$. 
        \end{definition}
        The following proposition characterizes another case where error bound conditions of problem holds.

        \begin{example}[inner loop linear convergence rate examples]\label{example:inn-lp-lin-cnvg}

>>>>

        \begin{align}
            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}, \label{def:inxt-apg:yk}
            & x_k \approx_{\epsilon_k} T_{L_k}(y_k), \label{def:inxt-apg:xk}

@@

            & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). \label{def:inxt-apg:vk}

@@

    \begin{proposition}[convergence with valid error schedule]\;\label{prop:inxt-apg-cnvg-generic}\\

@@

    Now, it only remains to determine the sequence $\alpha_k$ to derive a type of convergence rate for the algorithm because from the above theorem, we have the convergence rate $\beta_k$ and, the error parameters $\epsilon_k, \rho_k$ both controlled by the sequence $(\alpha_k)_{k \ge 0}$.

@@

                \beta_k = \frac{\alpha_k^2L_k}{\alpha_0^2L_0}

@@

        \begin{proposition}[$\mathcal O(1/k^2)$ outer loop function value convergence]\;\label{prop:opt-cnvg-outr-loop}\\

@@

    \subsection{The gradient mapping also shrinks}
        In this section, we show one extremely favorable properties and its assumptions such that, successive iterates $v_k, v_{k - 1}$ converges to zero as $k \rightarrow \infty$, and hence the norm of the gradient mapping converges at a rate of $\mathcal O(1/k)$. 
        This property will be crucial for analyzing the total complexity for the algorithm as a whole. 
        \begin{proposition}[iterates $v_k$ and gradient mapping]\;\label{prop:vk-gm}\\
            Assume there exists $\bar x \in \RR^n$ which is the minimizer of $F$ and, we set $\alpha_0 = 1$. 
            Then for the iterates generated $(y_k, x_k, v_k)_{k \ge 0}$ by the algorithm, for all $k \ge 0$ all followings are true. 
                \item\label{prop:vk-gm:result1} it has $v_k - v_{k - 1} = \alpha_k^{-1}(x_k - y_k) = \alpha_k^{-1}L_k^{-1} \mathcal G_{L_k}(y_k)$. 
                \item\label{prop:vk-gm:result2} as a consequence of the former, we have the following bound: 
                    \Vert \bar x - v_k\Vert \le \Vert \bar x - v_{- 1}\Vert
                        \frac{2 \mathcal E_0}{L_0} 
                        \sum_{n = 1}^{k} \frac{1}{n^p}
                    \right)^{1/2}. 
            \textbf{Our first result follows. }
            It has $y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}$ from \eqref{def:inxt-apg:yk}, and $v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1})$ from \eqref{def:inxt-apg:vk}. 
            Using this information we have 
                v_k - v_{k - 1} &=
                x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}) 
                - \alpha_k^{-1}(y_k - (1 - \alpha_k)x_{k - 1})
                &= (1 - \alpha_k^{-1})x_{k - 1} + \alpha_k^{-1}x_k - \alpha_k^{-1}y_k + (\alpha_k^{-1} - 1)x_{k - 1}
                &= \alpha_k^{-1}(x_k - y_k) = \alpha_k^{-1}L_k^{-1}L_k(x_k - y_k) = \alpha_k^{-1}L_k^{-1}\mathcal G_{L_k}(y_k). 
            \textbf{Our second result follows. }
            The assumption for Proposition \ref{prop:inxt-apg-cnvg-generic} are satisfied here hence: 
                0 &\le \beta_k\left(
                    \frac{L_0}{2}\Vert \bar x - v_{k - 1}\Vert^2
                - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
                - (F(x_k) - F(\bar x))
                \underset{(1)}\implies
                \frac{L_0}{2}\Vert \bar x - v_{k - 1}\Vert^2
                - \frac{\alpha_k^2L_k}{2\beta_k}\Vert \bar x - v_k\Vert^2
                &\underset{(2)}= 
                \frac{L_0}{2}\Vert \bar x - v_{k - 1}\Vert^2
                - \frac{L_0}{2}\Vert \bar x - v_k\Vert^2
                0 &\le \Vert \bar x - v_{-1}\Vert - \Vert \bar x - v_k\Vert
                    \frac{2 \mathcal E_0}{L_0}\sum_{n = 1}^{k}\frac{1}{n^p}
                \right)^{1/2}. 
            At (1), we assumed $\bar x$ is the minimizer so $- F(x_k) + F(\bar x) < 0$ and so we replaced it with a zero, and since $\beta_k > 0$ always we can divided on both side of the inequality without changing the sign. 
            At (2), we used $\beta_k = \frac{\alpha_k^2 L_k}{\alpha_0^2 L_0}$ from \eqref{ineq:lemma:opt-mmntm-seq-result2}, since we assumed $\alpha_0 = 1$ here it has $\beta_k = \alpha_k^2L_k/L_0$ hence the coefficient $\frac{\alpha_k^2L_k}{2 \beta_k} = \frac{L_0}{2}$. 
        Now, we will show the convergence rate of the normed gradient mapping is $\mathcal O(1/k)$ for the best chosen sequence. 
        The theorem that follows will acomplish that 
        \begin{theorem}[$\mathcal O(1/k)$ convergence of the gradient mapping]

        \end{theorem}
        \begin{proof}

@@

                \right)(F(x_k) - F(\bar x)), \text{ where } \frac{\gamma}{2\tau} \in (0, 1)

@@

                \item\label{prop:inn-loop-lin-cnvg:item3} The duality gap has a linear convergence rate by the inequality: 

@@

                \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. 

@@

        \end{remark}
        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]\;\\
            A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$. 
        \end{definition}
        The following proposition characterizes another case where error bound conditions of problem holds. 
        \begin{example}[inner loop linear convergence rate examples]\label{example:inn-lp-lin-cnvg}
